Expected Dependency Pair Match:\\ Predicting {HTER} improvements with expected syntactic structure

### 2009-05-12 mtjournal.tex
edits from mari.

Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system translation to
one or more reference (human) translations.
%
Automatic measures of this kind (e.g.\ BLEU \cite{papineni02bleu}) not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

The most popular evaluation measures are currently BLEU (based on
$n$-gram precision) and the edit-distance measure Translation Edit
Rate (TER) \cite{snover06ter}.  Recent research has found that these
measures may not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

@@

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \inlinecite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependent-based SParseval measure
\cite{roark06:sparseval}, originally designed as a parse-quality
metric for speech, is a similar approach, in that it is an F-measure
over a decomposition of reference and hypothesis trees.
\inlinecite{owczarzak07labelleddepseval} proposed \textbf{d} and
\textbf{d\_var} measures that compare LFG-derived relational tuples
from reference and hypothesis translations and reported substantial
improvement in correlation with human judgment relative to BLEU and
TER.

These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. Some \cite{liu05syntaxformteval,roark06:sparseval} use
PCFG parsers with deterministic head-finding, while others
\cite{owczarzak07labelleddepseval} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{roark06:sparseval,owczarzak07labelleddepseval} using a
widely-used and publically available PCFG parser and deterministic
head-finding rules.

>>>>

Machine translation (MT) evaluation is a challenge for research
because the space of good translations is large, and two equally good
translations may appear to be quite different at first glance. 
%
The challenges of choosing among translations are compounded when this
evaluation is done automatically.
%
Human evaluation, however, is both time-consuming and difficult, so
research has turned increasingly towards automatic measures of
translation quality, usually by comparing the system translation to
one or more reference (human) translations.
%
Automatic measures of this kind not
only provide a well-defined evaluation standard but are also required
for training on error criteria, e.g.\ with minimum error rate training
\cite{och03mert}.

Currently, the most popular evaluation measures include a measure
based on $n$-gram precision known as BLEU \cite{papineni02bleu}) and the edit-distance measure Translation Edit
Rate (TER) \cite{snover06ter}.  Recent research has found that these
measures may not accurately track translation quality both empirically
\cite{charniak03syntaxlmmt} and theoretically
\cite{callisonburch06bleuproblems}.

@@

As an alternative to these synonym- and paraphrase-based approaches,
other metrics model syntactically-local (rather than string-local)
word-sequences. \inlinecite{liu05syntaxformteval} compared tree-local
$n$-gram precision in various configurations of constituency and
dependency trees.  The dependent-based SParseval measure
\cite{roark06:sparseval}, designed as a parse-quality
metric for speech, is a similar approach, in that it is an F-measure
over a decomposition of reference and hypothesis trees.
\inlinecite{owczarzak07labelleddepseval} proposed \textbf{d} and
\textbf{d\_var} measures that compare LFG-derived relational tuples
from reference and hypothesis translations and reported substantial
improvement in correlation with human judgment relative to BLEU and
TER.

These syntactically-oriented measures require a system for proposing
dependency structure over the reference and hypothesis
translations. Some \cite{liu05syntaxformteval,roark06:sparseval} use
PCFG parsers with deterministic head-finding, while others
\cite{owczarzak07labelleddepseval} extract the semantic dependency
relations from an LFG parser \cite{cahill04lfg}.
%
This work extends the dependency-scoring strategies of
\inlinecite{roark06:sparseval} and \inlinecite{owczarzak07labelleddepseval} using a
widely-used and publically available PCFG parser and deterministic
head-finding rules.
